Measuring contrast processing in the visual system using the steady state visually evoked potential (SSVEP)

### 2025-01-30 review.qmd
Getting there... replaced  .pdf with .png but still not quite working

---
title: "Measuring contrast processing in the visual system using the steady state visually evoked potential (SSVEP)"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format:
  docx: 
    omitFigures: false
  pdf: default
    #keep-tex: true

@@

plt.tight_layout()
plt.savefig('Figures/1_centresurround.pdf')

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/2_linearsystem.pdf')

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/3_fullwaverectification.pdf')

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/4_transducer.pdf')

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/5_twoinputs.pdf')

@@

axs.set_title(f'Simulated sweep VEP at {nLevels} different contrasts', fontsize=10)
axs.semilogx(contrastRange, transducedSignal, 'o')
axs.semilogx(contrastRange[:4], reg.predict(X), 'r-', label='Linear Fit')
axs.semilogx(np.logspace(0.1,1.1,nLevels)/100, reg.predict(X2), 'r--')
axs.semilogx([x_intercept], [0], 'ro', label='Threshold')
axs.set_xlabel('Contrast')
axs.set_ylabel('Amplitude (a.u.)')
axs.set_xlim(0.01, 1)
axs.set_ylim(0, 10)
axs.legend()
axs.grid()
plt.tight_layout()
plt.savefig('Figures/6_sweepplot.pdf')

@@

# To save the figure
plt.savefig('Figures/7_clinicalplot.pdf')

@@

::: {.content-visible when-format="docx"}
![The perceived contrast of a stimulus depends on its context. A high contrast surround reduces the apparent contrast of the central 'probe' region.](Figures/1_centresurround.pdf){#fig-centresurround}
:::
::: {.content-visible unless-format="docx"}
![The perceived contrast of a stimulus depends on its context. A high contrast surround reduces the apparent contrast of the central 'probe' region.](Figures/1_centresurround.pdf){#fig-centresurround}
:::

>>>>

---
title: "Measuring contrast processing in the visual system using the steady state visually evoked potential (SSVEP)"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format:
  latex: default
  docx: 
    omitFigures: false
  pdf: default
    #keep-tex: true

@@

plt.tight_layout()
plt.savefig('Figures/1_centresurround.png', dpi=300)

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/2_linearsystem.png', dpi=300)

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/3_fullwaverectification.png', dpi=300)

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/4_transducer.png', dpi=300)

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/5_twoinputs.png', dpi=300)

@@

axs.set_title(f'Simulated sweep VEP at {nLevels} different contrasts', fontsize=10)
axs.semilogx(contrastRange, transducedSignal, 'o')
axs.semilogx(contrastRange[:4], reg.predict(X), 'r-', label='Linear Fit')
axs.semilogx(np.logspace(0.1,1.1,nLevels)/100, reg.predict(X2), 'r--')
axs.semilogx([x_intercept], [0], 'ro', label='Threshold')
axs.set_xlabel('Contrast')
axs.set_ylabel('Amplitude (a.u.)')
axs.set_xlim(0.01, 1)
axs.set_ylim(0, 10)
axs.legend()
axs.grid()
plt.tight_layout()
plt.savefig('Figures/6_sweepplot.png', dpi=300)

@@

# To save the figure
plt.savefig('Figures/7_clinicalplot.png', dpi=300)

@@

::: {.content-visible when-format="docx"}
![The perceived contrast of a stimulus depends on its context. A high contrast surround reduces the apparent contrast of the central 'probe' region.](Figures/1_centresurround.png){#fig-centresurround}
:::
::: {.content-visible unless-format="docx"}
![The perceived contrast of a stimulus depends on its context. A high contrast surround reduces the apparent contrast of the central 'probe' region.](Figures/1_centresurround.png){#fig-centresurround}
:::
